### 2014-08-03 Pero_Transcriptome.tex
added venn diagram

From the filtered assembly, I extracted putative coding sequences using Transdecoder version 16Jan2014 (\url{http://transdecoder.sourceforge.net/}). These putative protein coding sequences were annotated using default settings of the blastx algorithm \cite{Camacho:2009fc} against the SwissProt database downloaded on 1 March 2014. Because transcriptome assemblies typically contain non-coding elements (e.g. ncRNA) in addition to protein coding sequence, we annotated the entire filtered dataset using the NCBI nt dataset, downloaded on 1 March 2014. Lastly, because rapidly evolving nucleotide sequences may evade detection by blast algorithms, we used HMMER3 \cite{Wheeler:2013gj} to search for conserved protein domains contained in the Pfam database \cite{Punta:2012ko}. \\

@@

Transcriptome assembly for each tissue type was accomplished using the program Trinity. The raw assembly for brain, liver, testes and kidney contained 185425, 222096, 180233, and 514091 assembled sequences respectively. This assembly was filtered using a blast procedure with resulted in a final dataset containing 68331 brain-specific transcripts, 71041 liver-specific transcripts, 67340 testes-specific transcripts, and 113050 kidney-specific transcripts. Mapping the error-corrected adapter/quality trimmed reads to these datasets resulted in mapping 94.98\% (87.01\% properly paired) of brain-derived reads to the brain transcriptome, 96.07\% (88.13\% properly paired) of liver-derived reads to the liver transcriptome, 96.81\% (85.10\% properly paired) of testes-derived reads to the testes transcriptome, and 91.87\% (83.77\% properly paired) of kidney-derived reads to the kidney transcriptome. Together, these statistics suggest that the tissue-specific transcriptomes are of extremely high quality.

I then estimated gene expression on each of these tissue-specific datasets, which allowed me to understand expression patterns in the multiple tissues.

>>>>

From the filtered assembly, I extracted putative coding sequences using Transdecoder version 4ul2014 (\url{http://transdecoder.sourceforge.net/}). These putative protein coding sequences were annotated using default settings of the blastx algorithm \cite{Camacho:2009fc} against the SwissProt database downloaded on 1 March 2014. Because transcriptome assemblies typically contain non-coding elements (e.g. ncRNA) in addition to protein coding sequence, we annotated the entire filtered dataset using the NCBI nt dataset, downloaded on 1 March 2014. Lastly, because rapidly evolving nucleotide sequences may evade detection by blast algorithms, we used HMMER3 \cite{Wheeler:2013gj} to search for conserved protein domains contained in the Pfam database \cite{Punta:2012ko}. \\

@@

Transcriptome assembly for each tissue type was accomplished using the program Trinity. The raw assembly for brain, liver, testes and kidney contained 185425, 222096, 180233, and 514091 assembled sequences respectively. This assembly was filtered using a blast procedure with resulted in a final dataset containing 68331 brain-specific transcripts, 71041 liver-specific transcripts, 67340 testes-specific transcripts, and 113050 kidney-specific transcripts. Mapping the error-corrected adapter/quality trimmed reads to these datasets resulted in mapping 94.98\% (87.01\% properly paired) of brain-derived reads to the brain transcriptome, 96.07\% (88.13\% properly paired) of liver-derived reads to the liver transcriptome, 96.81\% (85.10\% properly paired) of testes-derived reads to the testes transcriptome, and 91.87\% (83.77\% properly paired) of kidney-derived reads to the kidney transcriptome. Together, these statistics suggest that the tissue-specific transcriptomes are of extremely high quality.  \\

I then estimated gene expression on each of these tissue-specific datasets, which allowed me to understand expression patterns in the multiple tissues {\hypertarget{Figure 1}{Figure 1}}.

%\vspace{5mm}
%\textbf{\hypertarget{Figure 1}{Figure 1}} \\
\centerline{\includegraphics[width=20.0\baselineskip]{/Users/macmanes/Documents/pero_transcriptome/venn.jpeg}}
\begin{quote}
\small{Figure 1. The Venn Diagram.}
\end{quote}
